Inducing Domain Specific Languages for Bayesian Program Learning

### 2018-02-02 paper.tex
ec references and start of circuit section

Our algorithm is best understood as inference in a hierarchical Bayesian model (Figure~\ref{graphicalModel}: solid lines):
A DSL $\mathcal{D}$
samples a latent program $p$
which determines the agent's observations, $x$.
This makes our work in instance of
 \emph{Bayesian Program
  Learning} (BPL; see~\citep{lake2013one,ellis2016sampling,DBLP:conf/icml/LiangJK10}).
In tandem we learn a learn a neural network $q$ that regresses
from observations to programs.
We will show that the interaction of
the generative and recognition models is important for solving these program induction problems.

%% We cast these problems as \emph{Bayesian Program
%%   Learning} (BPL; see~\citep{lake2013one,ellis2016sampling,DBLP:conf/icml/LiangJK10}),
%% where the goal is to infer from an observation $x$ a posterior distribution over programs, $\probability[p|x]$.
%% A DSL $\mathcal{D}$ specifies the vocabulary in which programs $p$ are written.
%% We equip our DSLs with a \emph{weight vector} $\theta$; together, $(\mathcal{D},\theta)$
%% define a probabilistic generative model over programs, $\probability[p|\mathcal{D},\theta]$.
%% In this BPL setting, $\probability[p|x]\propto \probability[x|p]\probability[p|\mathcal{D},\theta]$,
%% where the likelihood $\probability[x|p]$ is domain-dependent.
%% The solid lines in Fig.~\ref{graphicalModel} the diagram this generative model.
%% Alongside this generative model,
%% we infer a bottom-up recognition model, $q(x)$, which is a neural network that regresses from observations to a distribution over programs.

@@

\subsection{Boolean circuits}
pedagogical example; easy domain
\begin{figure}
  \includegraphics[width = \columnwidth]{figures/circuit.png} 
\end{figure}

>>>>

Our algorithm is best understood as inference in a hierarchical Bayesian model (Figure~\ref{graphicalModel}: solid lines):
A DSL $\mathcal{D}$
samples a latent program $p$
which determines the agent's observations, $x$.
This makes our work in instance of
 \emph{Bayesian Program
  Learning} (BPL; see~\citep{lake2013one,Dechter:2013:BLV:2540128.2540316,ellis2016sampling,DBLP:conf/icml/LiangJK10}).
In tandem we learn a learn a neural network $q$ that regresses
from observations to programs.
We will show that the interaction of
the generative and recognition models is important for solving these program induction problems.

TODO: talk explicitly about what ideas we are borrowing from EC
%% We cast these problems as \emph{Bayesian Program
%%   Learning} (BPL; see~\citep{lake2013one,ellis2016sampling,DBLP:conf/icml/LiangJK10}),
%% where the goal is to infer from an observation $x$ a posterior distribution over programs, $\probability[p|x]$.
%% A DSL $\mathcal{D}$ specifies the vocabulary in which programs $p$ are written.
%% We equip our DSLs with a \emph{weight vector} $\theta$; together, $(\mathcal{D},\theta)$
%% define a probabilistic generative model over programs, $\probability[p|\mathcal{D},\theta]$.
%% In this BPL setting, $\probability[p|x]\propto \probability[x|p]\probability[p|\mathcal{D},\theta]$,
%% where the likelihood $\probability[x|p]$ is domain-dependent.
%% The solid lines in Fig.~\ref{graphicalModel} the diagram this generative model.
%% Alongside this generative model,
%% we infer a bottom-up recognition model, $q(x)$, which is a neural network that regresses from observations to a distribution over programs.

@@

\subsection{Boolean circuits}
As a toy warm-up domain, we consider the problem of learning
to build the Boolean circuits out of logic gates.
Now, if we equipped our agent with a full repertoire of
circuit primitives -- XOR gates, multiplexers, etc. -- this problem would be easy,
and we could use sophisticated symbolic search algorithms like SMT solvers to synthesize circuits.
Instead, we gave \system only a NAND gate,
and tasked it with building a set of 500 random circuits made out of
AND, NOT, and OR gates.
This experimental setup was introduced in the original EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}.

Figure~\ref{circuitLearningCurve}

\begin{figure}
  \includegraphics[width = \columnwidth]{figures/circuit.png}
  \caption{\system learning to build Boolean circuits. We start out with only NAND gates and learn DSL that contains ...}\label{circuitLearningCurve}
\end{figure}
